---
title: "Lab 1 - Template"
author: "Your Group Name Here!"
date: "9/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Lab 1

Use the file  **RealEstateData1.csv** to answer the questions below.  


1.  (10 points) Clean and stylish.  

1.  (10 points)  Consider these variables:  **SalePrice, GrLivArea, X1stFlrSF, OverallQual, LotArea, and GarageArea.** For each variable, compute the following sample statistics:  the extremes, quartiles, mean, median, variance, standard deviation, range, and fourth spread (IQR). 

```{r}
data <- read.csv("RealEstateData1.csv", header = T)
```

```{r}
str(data)
```
```{r}
data[1:10, 1:4]
```

1. (10 points) Produce boxplots for these 5 variables **SalePrice, GrLivArea, X1stFlrSF, LotArea, and GarageArea**.  This should be five separate plots.  

```{r}

```


1. (10 points) Produce a grouped boxplot for **SalePrice** by **HouseStyle**.  Choose good colors.  

```{r}

```


1. (10 points) Produce histograms for the 6 variables **SalePrice, GrLivArea, X1stFlrSF, OverallQual, LotArea, and GarageArea**.  Choose good colors. 

```{r}

```


1.  (10 points) You could argue that one of the histograms isn't really a histogram.  Which one?  And if it's not a histogram, what is it?  


1. (10 points) Consider the variable **Fireplaces** and **TotRmsAbvGrd**. Does the mean value of **TotRmsAbvGrd** change for houses with 0, 1, 2, and 3 fireplaces? Does the minimum value of **TotRmsAbvGrd** change for houses with 0, 1, 2, and 3 fireplaces? Group by the variable **Fireplaces**, summarize the variable **TotRmsAbvGrd* and find out!

```{r}
data1 <- read.table("RealEstateData1.csv",sep=",", header = T,,stringsAsFactors = TRUE,na.strings = c("NA"))
```

```{r}
data2 <- read.table("RealEstateData1.csv",sep=",", header = T,stringsAsFactors = FALSE,na.strings = c("NA"))
```

```{r}
data3 <- read.table("RealEstateData1.csv",sep=",", header = T,stringsAsFactors = TRUE,na.strings = c("NA","."))
```
